Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
fixing predictions

```{r}
head(data.frame(summary(model_100)),-2)
```
```{r}
mcmc_trace(model_100)
mcmc_dens_overlay(model_100) #How can we just get a snapshot of our model evals?
```

@@

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state

@@

pred_100 <- data.frame(y_new = pred_100[-1])

ggplot(pred_100, aes(x=y_new))+geom_density()

summary(pred_100)

@@

```{r}
# For correlation check (type like model 2 from activity 19)
# Store the chains
model_100_df <- as.array(model_100) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_100_df <- model_100_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_100_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

>>>>

```{r}
head(data.frame(summary(model_100)),-2)
```
```{r}
mcmc_trace(model_100)
mcmc_dens_overlay(model_100) 
```

@@

# pred_5 <- posterior_predict(
#   model_5,
#   newdata = Finaldata, transform = TRUE)

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)

# prediction_summary(y = Finaldata$ChinaVirusInterest,
#   yrep = pred_5)
```

```{r}
### For predicting one case 
new_FL <- Finaldata%>% 
          filter(State=="FL") #filter the row of interest

@@

pred_2 <- data.frame(y_new = pred_FL[-1])

ggplot(pred_2, aes(x=y_new))+geom_density()

summary(pred_2)

@@

```{r}
# For correlation check (type like model 2 from activity 19)
# Store the chains
model_2_df <- as.array(model_2) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_2_df <- model_2_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_2_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```
